Flexibility of interactions depends on habitat suitability

### 2019-09-06 paper/manuscript.Rmd
reorganise beginning of methods

## Data aquisition

### Species interactions

@@

We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014]. 
This database contains datasets originating from `r length(interaction_citations$BIBTEXKEY)` studies published in the primary literature between `r int_citations_year_range[1]` and `r int_citations_year_range[2]` `r all_int_cites`.
All together, these data sources contained `r format(n_sp_names, big.mark = ",")` unique organism names; `r format(n_names_in_multiple_references_orig, big.mark = ",")` of them in more than one data source.
Because assessing how habitat suitability affects interaction partners of plants and pollinators requires linking of species across different datasets, it was important to ensure that the names used to identify species were as accurate as possible.
From the total number of organisms,`r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level_no_subsp, big.mark = ",")` to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, and no taxonomic information was avaliable for the remaining `r format(n_no_tax_info, big.mark = ",")`. 
As the species level was the most common taxonomic rank available in our interaction datasets, in all further analysis, we group together subspecies or varieties within a same species.

We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the cannonical names used to identify organisms (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`). 
We assessed the validity of a cannonical name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources. 
Specifically, we used the function `gnr_resolve` from the R package `taxize` `r as.character(packageVersion('taxize'))` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].

From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, we were able to identify and correct `r format(n_sp_corrected_typos, big.mark = ",")` spelling mistakes. 
These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with tgose in the Global Names Resover database. 
In rare occasions, the fuzzy matching algorithm can suggest a cannonical name that has similar spelling but that correspond to an organism in a completely different taxonomic group, often in a different kingdom. 
We, therefore, checked the taxonomic hierarchy of suggested names to confirm that it corresponded to our expectations. 
We retrieved all taxonomic hierarchies from the National Center for Biotechnology Information taxonomic database (https://www.ncbi.nlm.nih.gov/taxonomy).

>>>>

@@

We retrieved plant-pollinator networks from the Web of Life database [@fortuna_web_2014]. 
This database contains datasets originating from `r length(interaction_citations$BIBTEXKEY)` studies published in the primary literature between `r int_citations_year_range[1]` and `r int_citations_year_range[2]` `r all_int_cites`. 
Calculating the environmental stress of species in their community and their Eltonian niche breadth requires that the scientific names used to identify them are valid and unambiguous. 
This is because valid scientific names are necessary to both accurately match species across studies and to obtain other information from biological databases. 
However, a significant proportion of the data obtained contain spelling mistakes, taxonomic synonyms, or non-standard abbreviations. 
Therefore, our first step was to validate and correct scientific names across studies to ensure that we matching of species across studies was as accurate as possible.

Second, we calculated the suitability of the environment for a species in a particular community as a proxy of environmental stress. 
We assume that the environmental stress a species experience in a particular location is inversely related to the suitability of the average environmental conditions in that place. 
Our third and final step was to relate the environmental suitability to the relative number of partners a species has in a community, as a proxy for Eltionian niche breadth. 
To explore this relationship within and across species, we used a multilevel Bayesian model in which we controlled for the potential effects of the environment on co-occurrence.

## Plant-pollinator interactions

All together, interaction data from the included studies included `r format(n_sp_names, big.mark = ",")` unique organism names. 
From these `r format(n_names_in_multiple_references_orig, big.mark = ",")` were present in more than one study.
From the total number of organisms, `r format(n_sp_names_subsp_level, big.mark = ",")` were identified to the subspecies or variety level, `r format(n_sp_names_sp_level_no_subsp, big.mark = ",")` to the species level, `r format(n_sp_names_gen_level, big.mark = ",")` to the genus level, whereas the remaining `r format(n_no_tax_info, big.mark = ",")` were unidentified. 
As the species level was the most common taxonomic rank available in our interaction datasets, in all further analysis, we grouped together subspecies or varieties within a same species.

We were able to confirm the validity of `r format(n_sp_correct_in_data, big.mark = ",")` of the scientific names used to identify organisms (roughly `r scales::percent(n_sp_correct_in_data/n_sp_names_sp_level, 1)`). 
We assessed the validity of a name by querying the Global Names Resolver database (https://resolver.globalnames.org) which includes data from `r dplyr::n_distinct(taxize::gnr_datasources()$title)` taxonomic sources. 
Specifically, we used the function `gnr_resolve` from the R package `taxize` `r as.character(packageVersion('taxize'))` [@chamberlain_taxize_2013; @chamberlain_taxize_2019].

From the remaining `r format(n_sp_names_sp_level - n_sp_correct_in_data, big.mark = ",")` names we were unable to validate, we were able to identify and correct `r format(n_sp_corrected_typos, big.mark = ",")` that contained spelling mistakes. 
These spelling mistakes were corrected automatically by fuzzy matching the canonical names in our data sources with tgose in the Global Names Resover database. 
In rare occasions, the fuzzy matching algorithm can suggest a cannonical name that has similar spelling but that correspond to an organism in a completely different taxonomic group, often in a different kingdom. 
We, therefore, checked the taxonomic hierarchy of suggested names to confirm that it corresponded to our expectations. 
We retrieved all taxonomic hierarchies from the National Center for Biotechnology Information taxonomic database (https://www.ncbi.nlm.nih.gov/taxonomy).
